Negative Types

### 2014-05-23 ring.tex
typos

Consider the situation above in which we want to identify the spaces
corresponding to the types $(1-1)$ and the empty type:
\begin{center}
\begin{tikzpicture}
\node[above] at (0,0) {\pp};
\node[left] at (-0.2,0) {$1$};
\draw[fill] (0,0) circle [radius=0.05];
\node[above] at (2.6,0) {\mm};
\node[right] at (2.8,0) {$1$};
\draw[fill] (2.6,0) circle [radius=0.05];
\draw[->,red] (0.1,0) -- (2.5,0);
\draw[->,red] (-0.1,-0.1) arc (135:405:0.2);
\node[below,red] at (0,-0.4) {$\refl{1}$};
\draw[->,red] (2.5,-0.1) arc (135:405:0.2);
\node[below,red] at (2.6,-0.4) {$\refl{1}$};
\node[above] at (1.3,0) {$\seg{1}$};
\node[right] at (1.3,-0.5) {$q$};
%%
\node[below] at (1.3,-1.5) {$\emptyset$};
\draw[fill] (1.3,-1.5) circle [radius=0.05];
\draw[->,red] (1.4,-1.4) arc (-45:225:0.2);
\node[right,red] at (1.5,-1.3) {$\refl{0}$};
%% 
\draw[->,double,blue] (1.3,-0.1) -- (1.3,-1);
\end{tikzpicture}
\end{center}
The top of the figure is the 1-dimensional cube representing the type $(1-1)$
as before except that we now add a path $\seg{1}$ to connect the two
endpoints. (Note that previously, the dotted lines in the figures were a
visualization aid and were \emph{not} meant to represent paths.) We also make
explicit the trivial identity paths from every space to itself.  The bottom
of the figure is the 0-dimensional cube representing the empty type. The path
$\seg{1}$ identifies the two occurrences of 1. To express the
equivalence of $(1-1)$ and 0, we add a 2-path, i.e. a path between paths,
that asserts connects the path $\seg{1}$ to the trivial path
$\refl{0}$ on the empty type. That effectively makes the two points
``disappear.''  Surprisingly, that is everything that we need. The extension
to higher dimensions just ``works'' because paths in homotopy type theory
have a rich structure. We explain the details below.

>>>>

Consider the situation above in which we want to identify the spaces
corresponding to the types $(1-1)$ and the empty type:
\begin{center}
\begin{tikzpicture}
\node[above] at (0,0) {\pp};
\node[left] at (-0.2,0) {$1$};
\draw[fill] (0,0) circle [radius=0.05];
\node[above] at (2.6,0) {\mm};
\node[right] at (2.8,0) {$1$};
\draw[fill] (2.6,0) circle [radius=0.05];
\draw[->,red] (0.1,0) -- (2.5,0);
\draw[->,red] (-0.1,-0.1) arc (135:405:0.2);
\node[below,red] at (0,-0.4) {$\refl{1}$};
\draw[->,red] (2.5,-0.1) arc (135:405:0.2);
\node[below,red] at (2.6,-0.4) {$\refl{1}$};
\node[above] at (1.3,0) {$\seg{1}$};
\node[right] at (1.3,-0.5) {$q$};
%%
\node[below] at (1.3,-1.5) {$\emptyset$};
\draw[fill] (1.3,-1.5) circle [radius=0.05];
\draw[->,red] (1.4,-1.4) arc (-45:225:0.2);
\node[right,red] at (1.5,-1.3) {$\refl{0}$};
%% 
\draw[->,double,blue] (1.3,-0.1) -- (1.3,-1);
\end{tikzpicture}
\end{center}
The top of the figure is the 1-dimensional cube representing the type $(1-1)$
as before except that we now add a path $\seg{1}$ to connect the two
endpoints. (Note that previously, the dotted lines in the figures were a
visualization aid and were \emph{not} meant to represent paths.) We also make
explicit the trivial identity paths from every space to itself.  The bottom
of the figure is the 0-dimensional cube representing the empty type. The path
$\seg{1}$ identifies the two occurrences of 1. To express the equivalence of
$(1-1)$ and 0, we add a 2-path $q$, i.e. a path between paths, that connects
the path $\seg{1}$ to the trivial path $\refl{0}$. That effectively makes the
two points ``disappear.''  Surprisingly, that is everything that we need. The
extension to higher dimensions just ``works'' because paths in homotopy type
theory have a rich structure. We explain the details below.
